---
title: "1FloridaADRC Recruitment Report"
pdf_document: null
geometry: margin=1cm
output: pdf_document
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in,height=1.5in]{oneflorida.png}\LARGE\\}
  - \posttitle{\end{center}}

---
\fontfamily{arial}
\fontsize{10}{22}
\fontseries{}
\selectfont



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages= FALSE, warning= FALSE, comment=NA , fig.pos = "!H", out.extra = "")
library(tidyverse)
options(tidyverse.quiet = TRUE)
library(dotenv)
library(REDCapR)
library(knitr)
options(dplyr.summarise.inform = FALSE)
library(kableExtra)
```



```{r, targets}

targets<- read.csv("targets.csv")

all_sites_hispanic<- targets %>% 
  filter(Target== "Hispanic consented") %>% 
  tail(3) %>% 
  kbl(booktabs = T)

all_sites_white<- targets %>% 
  filter(Target== "White consented") %>% 
  tail(3) %>% 
  kbl(booktabs = T)

all_sites_african<- targets %>% 
  filter(Target== "African American consented") %>% 
  tail(3) %>% 
  kbl(booktabs = T)

all_sites_new<- targets %>% 
  filter(Target== "New Participants") %>% 
  tail(3) %>% 
  kbl(booktabs = T)

all_sites_fv<- targets %>% 
  filter(Target== "Follow-up visits") %>% 
  tail(3) %>% 
  kbl(booktabs = T)

all_sites_mripet<- targets %>% 
  filter(Target== "FV MRI/PET") %>% 
  tail(3) %>% 
  kbl(booktabs = T)

```

```{r results='asis', echo=FALSE}
cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.33\\linewidth}
    \\caption{Hispanic consented}",
        all_sites_hispanic,
    "\\end{minipage}%
    \\begin{minipage}{.31\\linewidth}
    \\caption{White non-hispanic consented}",
        all_sites_white,
    "\\end{minipage} 
     \\begin{minipage}{.32\\linewidth}
    \\caption{African American consented}",
        all_sites_african,
    "\\end{minipage} 
\\end{table}"
)) 
```


```{r results='asis', echo=FALSE}
cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.33\\linewidth}
    \\caption{New Participants Target}",
        all_sites_new,
    "\\end{minipage}%
    \\begin{minipage}{.33\\linewidth}
    \\caption{Follow-up Visits Target}",
        all_sites_fv,
    "\\end{minipage} 
    \\begin{minipage}{.33\\linewidth}
    \\caption{Follow-up Visits MRI/PET}",
       all_sites_mripet ,
    "\\end{minipage} 
\\end{table}"
)) 
```

Tables 1-6- This table displays the P30 grant proposal aims as outlined on page 359, second paragrapgh on the P30 Submitted Application, (https://www.dropbox.com/s/bxelgas81y4embo/P30%20Submitted%20Application.pdf?dl=0). The tables are described as followed: 1) Target recruitment of approximately (~) 40% of all participants are to be Hispanic for all sites, 2) Target recruitment of approximately (~) 40% of all participants are to be White non-hispanic for all sites, 3) Target recruitment of approximately (~) 20% of all participants are to be African American for all sites, 4) Target recruitment of 100 new participants are to be consented at each site (MSMC, UM, UF), 5) Target follow-up visits are to be 200 follow-up visits for MSMC, 100 follow-up visits for UF, and 100 follow-up visits for UF, 6) Follow-up participant target activity is to receive repeat MRI and PET scans.
  